
\documentclass[11pt]{article}
\usepackage{palatino}
\usepackage{supertabular}
\usepackage{float}
\usepackage{pifont}
\usepackage{url}
% \usepackage{bookman}

% \setlength{\voffset}{-25mm}
\textheight 9.3in         % 1in top and bottom margin
\textwidth 6.5in        % 1in left and right margin

\oddsidemargin 0in      % Both side margins are now 1in
\evensidemargin 0in

% The header goes .5in from top of the page and from the text.
\topmargin -.7in
\headsep .5in
\marginparwidth .7in
\marginparsep .15in

\begin{document}

\pagestyle{empty}

%\begin{center}
{\noindent\huge\bf Stephanos Matsumoto}
%\end{center}

\vspace{4mm}
%\noindent(This CV is also available at \texttt{http://www.stevematsumoto.net/cv}.)

\begin{table}[h]
  \centering
  \begin{tabular}{p{0.5\linewidth}p{0.5\linewidth}}
    ETH Zurich, Network Security Group & Email: \verb+steve@stevematsumoto.net+\\
    CAB F56.1 & Phone: +41 44 632 45 50\\
    Universit\"{a}tstrasse 6 & \verb+http://www.stevematsumoto.net/+\\
    8092 Zurich, Switzerland &\\
  \end{tabular}
\end{table}

%--------------------------------------------------------------------------------
{\noindent\Large\textbf{Research Areas}}\\\\
Decentralized Internet-scale network architectures, public-key infrastructures,
authentication and trust, blockchains, future Internet architecture, incentives
and economic issues, network security

%--------------------------------------------------------------------------------
\begin{tabbing}
\quad\=\kill
{\Large\textbf{Education}}\\\\
Department of Computer Science, ETH Zurich, Switzerland.\\
\>Ph.D., Computer Science, January 2014 -- Present.\\
\>Advisor: Prof.\ Adrian Perrig.\\\\

Department of Electrical and Computer Engineering, Carnegie Mellon University,
Pittsburgh, PA.\\
\>Ph.D., Electrical and Computer Engineering, June 2012 -- Present.\\
\>Advisor: Profs.\ Adrian Perrig, Virgil Gligor.\\\\

Department of Electrical and Computer Engineering, Carnegie Mellon University,
Pittsburgh, PA.\\
\>M.S., Electrical and Computer Engineering, June 2012 -- August 2013.\\
\>Thesis: A Scalable and Trustworthy Entity Validation Infrastructure.\\
\>Advisor: Prof.\ Adrian Perrig.\\\\

Harvey Mudd College, Claremont, CA.\\
\>B.S., Joint Major in Mathematics and Computer Science, September 2008 -- May
2012.\\
\>\emph{Graduated with High Distinction, Departmental Honors in Computer
Science.}\\\\

College of the Canyons, Santa Clarita, CA\\
\>A.A., Mathematics, August 2005 -- May 2008.\\
\>\emph{Graduated with High Honors.}
\end{tabbing}

\newcounter{refs}
\setcounter{refs}{1}
\makeatletter
\newcommand{\theref}{\@arabic\c@refs}
\makeatother

\renewcommand{\refname}{Refereed Conference and Workshop Papers} % ***
\begin{thebibliography}{77}

\bibitem[\theref]{chen2015ecodns}
  Chen Chen, Stephanos Matsumoto, Adrian Perrig.
\newblock ``ECO-DNS: Expected Consistency Optimization for DNS.''
\newblock In \emph{35th IEEE International Conference on Distributed Computing
Systems (ICDCS)}, Columbus, OH, July 2015.
\stepcounter{refs}

\bibitem[\theref]{matsumoto2015deployment}
  Stephanos Matsumoto, Pawel Szalachowski, Adrian Perrig.
\newblock ``Deployment Challenges in Log-Based PKI Protocols.''
\newblock In \emph{Eighth European Workshop on System Security (EuroSec 2015)},
Bordeaux, France, April 2015.
\stepcounter{refs}

\bibitem[\theref]{matsumoto2015certificates}
  Stephanos Matsumoto, Raphael M. Reischuk.
\newblock ``Certificates-as-an-Insurance: Incentivizing Accountability in
SSL/TLS.''
\newblock In \emph{NDSS Workshop on Security of Emerging Network Technologies
(SENT '15)}, San Diego, CA, February 2015.
\stepcounter{refs}

\bibitem[\theref]{szalachowski2014policert}
  Pawel Szalachowski, Stephanos Matsumoto, Adrian Perrig.
\newblock ``PoliCert: Secure and Flexible TLS Certificate Management.''
\newblock In \emph{ACM Conference on Computer and Communications Security (CCS
'14)}, Scottsdale, AZ, November 2014.
\stepcounter{refs}

\bibitem[\theref]{matsumoto2014fleet}
  Stephanos Matsumoto, Samuel Hitz, Adrian Perrig.
\newblock ``Fleet: Defending SDNs from Malicious Administrators.''
\newblock In \emph{ACM SIGCOMM Workshop on Hot Topics in Software Defined
Networking (HotSDN '14)}, Chicago, IL, August 2014.
\stepcounter{refs}

\bibitem[\theref]{Lea:pixellaser-tepra}
M. Leece, N. Lesperance, S. Matsumoto, M. Korbel, K. Lei, Z. Dodds.
\newblock ``PixelLaser: Evaluating Monocular Range from Texture.''
\newblock In \emph{IEEE International Conference on Technologies for Practical
Robot Applications (TePRA '11)}, Boston, MA, April 2011.
\stepcounter{refs}

\bibitem[\theref]{Lea:pixellaser-isvc}
N. Lesperance, M. Leece, S. Matsumoto, M. Korbel, K. Lei, Z. Dodds.
\newblock ``PixelLaser: Computing Range from Monocular Texture.''
\newblock In \emph{Proceedings of the 6th International Symposium on Visual
Computing (ISVC '10)}, Las Vegas, NV, December 2010.
\stepcounter{refs}
\end{thebibliography}

%--------------------------------------------------------------------------------
\renewcommand{\refname}{Preprints}
\begin{thebibliography}{77}
\bibitem[\theref]{matsumoto2015designing}
  Stephanos Matsumoto, Raphael M. Reischuk, Pawel Szalachowski, Tiffany Hyun-Jin
  Kim, Adrian Perrig.
\newblock ``Designing a Global Authentication Infrastructure.''
\newblock arXiv:1506.03392 [cs.CR], June 2015.
\stepcounter{refs}
\end{thebibliography}

\renewcommand{\refname}{Posters}
\begin{thebibliography}{77}
\bibitem[\theref]{Cea:android-im}
Adam Cozzette, Kathryn Lingel, Steve Matsumoto, Oliver Ortlieb, Jandria
Alexander, Joseph Betser, Luke Florer, Geoff Kuenning, John Nilles, and Peter
Reiher.
\newblock ``Improving the Security of Android Inter-Component Communication.''
\newblock IFIP/IEEE Symposium on Integrated
Network Management, May 2013.\\
\stepcounter{refs}

\bibitem[\theref]{kelley2013art}
Patrick Gage Kelley, Saranga Komanduri, Stephanos Matsumoto, Michelle L.
Mazurek, Richard Shay, Blase Ur, Timothy Vidas, Lujo Bauer, Nicolas Christin,
and Lorrie Faith Cranor.
\newblock ``The Art of Password Creation.''
\newblock IEEE Symposium on Security and Privacy, May 2013.\\
\stepcounter{refs}

\bibitem[\theref]{matsumoto2011what}
Steve Matsumoto.
\newblock ``What do random walks tell us about the shapes of regions in the
complex plane?''
\newblock Harvey Mudd College Celebration of Student Research, September 2011.\\
\stepcounter{refs}
\end{thebibliography}

%\newpage
\noindent{\Large\textbf{Teaching}}\\

\noindent Future Faculty Program (transcript available upon request).\\
Carnegie Mellon University, Fall 2012--Spring 2016.
\vspace{2mm}

\noindent Teaching Assistant and Course Coordinator, Network Security.\\
Instructors: Prof. Adrian Perrig; Drs.\ Thomas D\"{u}bendorfer, Stefan Frei.\\
Department of Computer Science, ETH Zurich, Fall 2015.
\vspace{2mm}

\noindent Bachelor's Thesis Supervisor (co-advisor with Adrian Perrig).\\
Student: Samuel Steffen.\\
Department of Computer Science, ETH Zurich, Spring/Summer 2015.
\vspace{2mm}

\noindent Teaching Assistant, Network Security.\\
Instructors: Profs.\ Bernhard Plattner, Adrian Perrig; Drs.\ Thomas
D\"{u}bendorfer, Stefan Frei.\\
Department of Electrical Engineering, ETH Zurich, Fall 2014.
\vspace{2mm}

\noindent Teaching Assistant, Information Security.\\
Instructors: Profs. Srdjan Capkun, Adrian Perrig.\\
Department of Computer Science, ETH Zurich, Spring 2014.
\vspace{2mm}

\noindent Teaching Assistant, 18-202: Mathematical Foundations of Electrical
Engineering.\\
Instructors: Profs. Li Yuo, Tom Sullivan.\\
Department of Electrical and Computer Engineering, Carnegie Mellon University,
Fall 2013.
\vspace{2mm}

\noindent Teaching Assistant, 18-202: Mathematical Foundations of Electrical
Engineering.\\
Instructor: Prof. Xin Li.\\
Department of Electrical and Computer Engineering Department, Carnegie Mellon
University, Spring 2013.\\
\vspace{2mm}

\noindent{\Large\textbf{Awards}}\\

\noindent NSF Graduate Fellowship,
2012 -- present (on reserve from 2015)
\vspace{2mm}

\noindent Cecil H. Short Memorial Prize,
Pomona College, 2012
\vspace{2mm}

\noindent National Physical Science Consortium Graduate Fellowship,
National Security Agency, 2012
\vspace{2mm}

\noindent Honorable Mention, Ford Foundation Predoctoral Fellowship,
2012
\vspace{2mm}

\noindent International Vacation Scholarship,
University of South Australia, 2011
\vspace{2mm}

\noindent Harvey Mudd College Rose Hills Grant,
Rose Hills Foundation, 2010, 2011
\vspace{2mm}

\noindent Rose Hills Foundation Science and Engineering Scholarship,
2009--2012
\vspace{2mm}

\noindent Ebell/Flint Scholarship,
The Ebell of Los Angeles, 2009--2012
\vspace{2mm}

\noindent Dean's List,
Harvey Mudd College, 2009--2011
\vspace{2mm}

\noindent Harvey Mudd Merit Award,
Harvey Mudd College, 2008--2012
\vspace{2mm}

\end{document}
%--------------------------------------------------------------------------------
%--------------------------------------------------------------------------------
%--------------------------------------------------------------------------------
